Simultaneous Elicitation of Scoring Rule and Agent Preferences for Robust Winner Determination

### 2020-10-07 minimax.tex
adjusted tables and figures

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
It admits a parameter $\pi \in [0, 1]$.
This strategy first decides whether it will ask a question about weights (probability $\pi$) or a question about a preference ordering (probability $1-\pi$). If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$. The intervals are initialized to $[1, n]$. If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.

@@

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {L.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.06 & 0.49 & 6.17 & 0.78 & 5.85 & 0.87& 6.32 & 0.61\\
			40 & 7.35 & 0.82 & 2.98 & 0.99 & 2.57 & 1.05 & 3.37 & 0.83\\
			60 & 5.74 & 1.03 & 0.77 &0.78 & 0.67 & 0.67 & 2.33 & 1.05\\
			80 & 4.10 & 1.15 & 0.05 & 0.18 & 0.03 & 0.12 & 2.28 & 1.05\\
			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average MMR in problems of size $(5, 10)$ after $k$ questions and $200$ runs.}
	\label{tab:comparison}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average MMR after $k$ questions with Limited Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{MMR}$} & {$m\cdot n +m^?$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  \\
			5 & 15 & 1.5 & 80 &  \\
			5 & 20 & 2.0 & 110 &  \\
			10 & 20 & 2.0 & 340 &  \\
			10 & 30 & 3.0 & 527 &  \\
			15 & 30 & 3.0 &  &  \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{}
	\label{tab:linearity}
\end{table}

@@

We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions. We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random). Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
%Finally in Table \ref{fig:p}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 &  &  &  &  \\
			50 &  &  &  &  \\
			100 &  &  &  &  \\
			150 &  &  & &  \\
			200 &   &  &  &  \\
			250 &  & &  &  \\
			300 &&&& \\
			350 &&&& \\
			400 &&&& \\
			450 &&&& \\
			500 &&&& \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
	\label{tab:twoP}
\end{table}

>>>>

The \strat{Random} strategy gives a baseline for comparison and informs about the difficulty of an elicitation problem. 
This strategy first chooses equiprobably whether it will ask a question about weights or a question about a preference ordering. If it opted for a question about weights, it draws one rank in $1 ≤ r ≤ m-2$ equiprobably, takes the middle of the interval of values for $\lambda$ that are still possible considering our knowledge so far, and asks whether $w_r - w_{r+1} ≥ \lambda (w_{r+1} - w_{r+2})$. The intervals are initialized to $[1, n]$. If it opted for a question to agents, it draws equiprobably among the agents whose preference is not known entirely; draws an alternative $a$ equiprobably among those involved in some incomparabilities in $\ppref_j$; and draws an alternative $b$ equiprobably among those incomparable with $a$ in $\ppref_j$.

@@

\subsection{Our previous presentation}
\sisetup{round-mode=places, round-precision=2, table-figures-integer=2, table-figures-decimal=2}
\begin{table}
	\begin{center}
		\resizebox{\columnwidth}{!}{
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{k} & {Rnd.} & {sd} & {Pes.} & {sd} & {Ex.\ pes.} & {sd} & {Eli.} & {sd} \\
			\midrule
			0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0 & 10.0 & 0.0\\
			20 & 9.06 & 0.49 & 5.85 & 0.87 & 6.17 & 0.78 & 6.32 & 0.61\\
			40 & 7.35 & 0.82 & 2.57 & 1.05 & 2.98 & 0.99 & 3.37 & 0.83\\
			60 & 5.74 & 1.03 & 0.67 & 0.67 & 0.77 &0.78 & 2.33 & 1.05\\
			80 & 4.10 & 1.15 & 0.03 & 0.12 & 0.05 & 0.18 & 2.28 & 1.05\\
			100 & 2.63 & 1.19 & 0.0 &  0.0 & 0.0 & 0.0& 2.28 & 1.05\\
			\bottomrule
		\end{tabular}
		}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(5, 10)$ after $k$ questions and $200$ runs.\commentBN{Attention, I already corrected the table with the new names. The column Pes. here is the Limited Pessimistic, I inverted them to follow the presentation order.}}
	\label{tab:comparison}
\end{table}

@@

\begin{figure}
	\centering
	\includegraphics[width=.45\textwidth]{linearity.png}
	\caption{Average $\MMR$ after $k$ questions with Pessimistic strategy after 10 runs for different problem sizes.}
	\label{fig:linearity}
\end{figure}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-number-alignment = center]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]S[table-figures-integer=1, table-number-alignment = center, table-figures-decimal=0]}
			\toprule
			{m} & {n} & {$\frac{n}{10}$} & {$k_{\MMR}$} & {$m\cdot n +m^?$} \\
			\midrule
			5 & 10 & 1.0 & 60 &  \\
			5 & 15 & 1.5 & 80 &  \\
			5 & 20 & 2.0 & 110 &  \\
			10 & 20 & 2.0 & 340 &  \\
			10 & 30 & 3.0 & 527 &  \\
			15 & 30 & 3.0 &  &  \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Number of questions needed by Pessimistic strategy to reach $\MMR=\frac{n}{10}$ (represented by $k_{\MMR}$), for different problem sizes.}
	\label{tab:linearity}
\end{table}

@@

We observe that the Pessimistic strategy is able to reduce the regret almost completely after $30$ questions. We also see that Limited pessimistic performs almost as well as Pessimistic; this is good news since (for $m=5$ and $n=5$), the former strategy is much faster and takes only $2.6s$ for a complete elicitation session, while the latter takes $16s$.
%However, it takes $1000$ times more time than the \strat{Random} strategy ($16s$ of the Pessimistic compared to $0.014s$ of the Random). Moreover, the results of the \strat{Limited pessimistic}, that takes almost $80\%$ less of the time of the \strat{Pessimistic} ($2.6s$), are essentially the same.
%In Table \ref{fig:1020}, we can see the drop of regret using a bigger instance.
%Finally in Table \ref{fig:p}
%
%\begin{table}
%	\begin{center}
%		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
%			\toprule
%			{p} & {Comm. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
%			\midrule
%			0 & 0.48 &0.59 & 0.48 &0.59  \\
%			50 & 0.01 & 0.04& 0.0 & 0.0 \\
%			100 & 0.04 & 0.09 & 0.13 & 0.35 \\
%			150 & 0.68 & 0.65 & 0.66 & 0.77 \\
%			200 &   &  &  &  \\
%			250 & 3.2 & 1.67 & 4.07	& 1.51 \\
%			300 &&&& \\
%			350 &&&& \\
%			400 &&&& \\
%			450 &&&& \\
%			500 &&&& \\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Average regret in problems of size $(10, 20)$ after $500$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair.}
%	\label{tab:twoP500}
%\end{table}

\begin{table}
	\begin{center}
		\begin{tabular}{S[table-figures-integer=3, table-number-alignment = right, table-figures-decimal=0]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]S[table-number-alignment = right]@{ ± }S[table-number-alignment = left]}
			\toprule
			{p} & {Com. Fst.} & {sd} & {Vot. Fst.} & {sd} \\
			\midrule
			0 & 0.66 & 0.67 & 0.65 & 0.65  \\
			50 & 1.23 & 1.46 & 0.8 & 0.79 \\
			100 & 2.03 & 1.56 &  &  \\
			150 & 3.41 & 1.79 & 4.07 & 1.51 \\
			200 &   &  &  &  \\
			250 & 8.4 & 1.86 & 	& \\
			300 &&&& \\
			350 &&&& \\
			400 &&&& \\
			\bottomrule
		\end{tabular}
	\end{center}
	\caption{Average $\MMR$ in problems of size $(10, 20)$ after $400$ questions and $10$ runs. Where $p$ represents the number of questions asked to the chair. (The $\MMR$ after 400 questions with Pessimistic is $0.62$ ± $0.56$)}
	\label{tab:twoP400}
\end{table}
